---
pagetitle: "Marie Curie"
output:
  bookdown::html_document2:
    css: ["files/style.css", 
          "https://use.fontawesome.com/releases/v5.7.2/css/all.css",
          "https://cdn.rawgit.com/jpswalsh/academicons/master/css/academicons.min.css"]
    number_sections: false
    # when knitting to html for pdf print set toc option to false
    toc: false
    toc_float: true
    selfcontained: true
    includes:
      in_header: "files/header.html"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(knitr)
library(kableExtra)
library(RefManageR)
library(googlesheets4)

# bibliography items 
publications <- "files/curie.bib"

# CV items can be read from an excel sheet
#cv_entries <- readxl::read_xlsx("files/cv_entries.xlsx")
#cv_entries <- subset(cv_entries, show == T)

# or CV items can be read from a google sheet using the sheet id
# use sheets_deauth() when the sheet can be viewed by anyone with the link
googlesheets4::sheets_deauth()
cv_entries <- googlesheets4::read_sheet("1bzHcV8x1I4Z7tOA52dkKLEh27gUR39R3NelefmdrKgw", col_types = "c")
cv_entries <- subset(cv_entries, show == T)

# all entries should have at least a year_begin and a what
cv_entries <- subset(cv_entries, !is.na(year_begin) & !is.na(what))

# general formatting
cv_entries$year <- str_c(cv_entries$year_begin, " --- ", cv_entries$year_end)
cv_entries[is.na(cv_entries$year), "year"] <- cv_entries[is.na(cv_entries$year), "year_begin"]
cv_entries <- arrange(cv_entries, desc(pmax(year_end, year_begin, na.rm = T)), desc(year_begin), desc(month_begin)) 
```

```{r helpers, include=F}

# formatting positions with long descriptions
longDesc <- function(data, showDesc = F){
  data %>%
  mutate(what = str_c("<span class='work-title'>", 
                      what, "</span><br> _", where, "_")) %>%
    
  mutate(what = ifelse(!is.na(description) & showDesc == T, 
                       str_c(what, "<br class='work-break'>", description), what)) %>%
  select(year, what) %>%
  kable(escape = F) %>%
  {tryCatch({
    column_spec(., 1, width_min = "9em") 
  }, error = function(e) NA)} 
}

# function to check whether a section should be hidden from output 
dontPrint <- function(data, forceDontPrint = F){
  # do various checks to determine if a section should be printed.
  # setting overridePrint = T means that no matter what the results of the checks, 
  # section will not be printed. 
  
  # note: even if not printed, section data will be present in the html output, just commented out.
  # do not use this function to hide private data, as it will be accessible in the html.
  
  dontPrint = F
  
  # don't print empty sections
  if(dim(data)[1] == 0){dontPrint = T}
  if(is.null(data)){dontPrint = T}
    
  return(dontPrint | forceDontPrint)
}

```

<div class="printOnly">
<a class="printTitle">Marie Curie</a>  
mariecurie<i class="fas fa-at fa-xs"></i>ens.fr 
</div>


<div>
## Contact {.invisible}  
</div>

<div class = "row">
<div class = "col-md-6">


Some stuff about me:

 * I poisoned myself doing research.
 * I was the first woman to win a Nobel prize
 * I was the first person and only woman to win a Nobel prize in two different sciences.
 
 
</div>


<div class = "col-md-6">
```{block type='col-6 grid-item', echo=TRUE}
<div class="info-box">

| Center | Left |
|:------:|:-----|
| <i class="fas fa-map-marker-alt"></i>|School of Physics & Chemistry,\
École Normale Supérieure|
| <i class="fas fa-envelope"></i> | mariecurie<i class="fas fa-at fa-sm"></i>ens.fr |
| <i class="ai ai-orcid ai-1x"></i> | [ORCID](https://orcid.org/<orcid-id>) |
| <i class="fab fa-github"></i> | [mariecurie](https://github.com/<github-user>) |


</div>
```
</div>
</div>




`r if( dontPrint(cv_entries %>% filter(type == 'education')) ){"<!--"}`
***
## Education {.nohead}
```{r education}
cv_entries %>% 
  filter(type == 'education') %>% 
  #mutate(year = str_c(year_begin, " --- ", year_end)) %>% 
  arrange(desc(year_end)) %>%
  select(year, what, where) %>% 
  kable(format = "html", align = "llr") %>% 
  {tryCatch({
    column_spec(., 3, italic = T, width_min = "12em") %>%
    column_spec(1, width_min = "12em")
  }, error = function(e) NA )}

```
`r if( dontPrint(cv_entries %>% filter(type == 'education')) ){"-->"}`




***
## Publications {.nohead}
```{r pubs-setup}
snatchPrint <- function(bib){
  # extract data from bibentry
  DOIs <- bib$doi
  refsList <- capture.output(PrintBibliography(bib))
    
  # add delim, and split entries
  refsList[which(nchar(refsList) == 0)] <- "<DELIM>"
  
  paste0(refsList, collapse = " ") %>% 
    strsplit(split = "<DELIM>") %>%
    unlist() -> entries
  
  # bold a name
  entries <- gsub("M Sklodowska-Curie", "__M Sklodowska-Curie__",
                  fixed = T, entries)
  entries <- gsub("M Curie", "__M Curie__", 
                  fixed = T, entries)
  
  # remove numeric if necessary
  entries <- gsub('\\[[[:digit:]]+\\] ', '', entries)
  
  # build doi link
  links <- paste0("https://www.doi.org/", DOIs)
  
  return(data.frame(what = entries, paperLink = links))
}

oops <- BibOptions(bib.style = "numeric", match.author = "exact",
                   max.names = 99, first.inits = FALSE, style = "text",
                   no.print.fields = c("doi","url","urldate", "issn"))


refs <- ReadBib(publications) 
NoCite(refs)
refs <- snatchPrint(refs)
```

`r if( dontPrint(refs) ){"<!--"}`
```{r publications}
refs %>% 
  select(what) %>%
  kable() 
```
`r if( dontPrint(refs) ){"-->"}`



`r if( dontPrint(cv_entries %>% filter(type == 'talks_and_posters')) ){"<!--"}`
*** 
## Talks & Posters {.nohead}
```{r talks_and_posters}
cv_entries %>% 
  filter(type == 'talks_and_posters') %>% 
  mutate(what = str_c(what, ", ", where)) %>%
  select(year_begin, what, description) %>% 
  arrange(desc(year_begin)) %>% 
  kable(format = "html", align = "llr") %>% 
  {tryCatch({
    column_spec(., 1, width_min = "4em") %>%
    column_spec(3, width_min = "6em", italic = T) 
  }, error = function(e) NA )}

```
`r if( dontPrint(cv_entries %>% filter(type == 'talks_and_posters')) ){"-->"}`




`r if( dontPrint(cv_entries %>% filter(type == 'service')) ){"<!--"}`
***
## Service {.nohead}
```{r service}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(what = str_c(what, ", ", where)) %>%
  select(what) %>% 
  kable()
```
`r if( dontPrint(cv_entries %>% filter(type == 'service')) ){"-->"}`




`r if( dontPrint(cv_entries %>% filter(type == 'awards')) ){"<!--"}`
***
## Grants & Awards {.nohead}
```{r awards}
cv_entries %>% 
  filter(type == 'awards') %>% 
  select(year_begin, what) %>% 
  arrange(desc(year_begin)) %>% 
  kable() %>%
  {tryCatch({
    column_spec(., 1, width_min = "4em") 
  }, error = function(e) NA )}

```
`r if( dontPrint(cv_entries %>% filter(type == 'awards')) ){"-->"}`




`r if( dontPrint(cv_entries %>% filter(type == "affiliations")) ){"<!--"}`
***
## Memberships & Affiliations {.nohead}
```{r affiliations}
cv_entries %>% 
  filter(type == "affiliations") %>% 
  longDesc() 
```
`r if( dontPrint(cv_entries %>% filter(type == "affiliations")) ){"-->"}`





`r if( dontPrint(cv_entries %>% filter(type == 'teaching')) ){"<!--"}`
***
## Teaching {.nohead}
```{r teaching}
cv_entries %>% 
  filter(type == 'teaching') %>% 
  longDesc() 
```
`r if( dontPrint(cv_entries %>% filter(type == 'teaching')) ){"-->"}`





`r if( dontPrint(cv_entries %>% filter(type == 'work')) ){"<!--"}`
***  
## Selected work experience {.nohead}
```{r work}
cv_entries %>% 
  filter(type == 'work') %>% 
  longDesc()
```
`r if( dontPrint(cv_entries %>% filter(type == 'work')) ){"-->"}`






`r if( dontPrint(cv_entries %>% filter(type == 'volunteering')) ){"<!--"}`
***
## Personal skills & volunteering {.nohead}
```{r volunteering}
cv_entries %>%
  filter(type == 'volunteering') %>%
  longDesc(showDesc = T)
```
`r if( dontPrint(cv_entries %>% filter(type == 'volunteering')) ){"-->"}`


